\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)

### 2021-06-30 authors_responses/first_tac_rejection/authors_response.tex
Used ieee bib settings to add et al for long references and some baselineskips to make the work fit on 12 pages Changed plot colours to match the matplotlib colours Fixed typoes throughout (response and revision) Still need to rerun simulation and update the hardware and execution parameters of new run

However, during only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter. We have now relaxed the requirements of the system model and no specify the prediction equations of EKF specifically.

@@

As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearising filter for the prediction step of the algorithm. However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag) and has been computed when evaluating the proposed filter through simulation. This can be done in various ways specific to the system being modelled and is beyond the scope of this work.

@@

We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer. To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer that the proposed filter performs very similarly. The computational performance is more difficult to compare. Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript). Future work is being done on a similarly modified EIF which can use a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.

>>>>

However, during only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter. We have now relaxed the requirements of the system model and no longer require prediction to be performed by an EKF specifically.

@@

As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearising filter for the prediction step of the algorithm. However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag) and has been used when evaluating our proposed filter through simulation. This can be done in various ways specific to the system being modelled and is beyond the scope of this work.

@@

We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer. To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer that the proposed filter performs very similarly. The computational performance is more difficult to compare. Comparison with a different encryption scheme would require another scheme meeting LCAO (needed to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript). Future work is being done on a similarly modified EIF which can use a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.
